An Embedding Framework for the Design and Analysis of Consistent Polyhedral Surrogates

### 2024-02-07 poly-embed-journal/poly-embed-journal-camera-ready.tex
Camera ready version

\documentclass[twoside,11pt]{article}
\usepackage[natbib,preprint]{jmlr2e}
\PassOptionsToPackage{numbers, compress, sort}{natbib}
\usepackage[margin=1.1in]{geometry}

@@

\usepackage{mathtools, amsmath, amssymb, graphicx, verbatim}
%\usepackage{amsthm}
%\usepackage[thmmarks, thref, amsthm]{ntheorem}
\usepackage{color}
\definecolor{darkblue}{rgb}{0.0,0.0,0.2}
\definecolor{darkgreen}{rgb}{0.0,0.3,0.0}
\hypersetup{colorlinks,breaklinks,
            linkcolor=darkblue,urlcolor=darkblue,
            anchorcolor=darkblue,citecolor=darkblue}
\usepackage{wrapfig}
\usepackage[font=small]{caption}
\usepackage{subcaption}
\usepackage[colorinlistoftodos,textsize=tiny]{todonotes} % need xargs for below
%\usepackage{accents}
\usepackage{bbm}
\usepackage{xspace}

@@

\usetikzlibrary{calc}
\newcommand{\Comments}{0}
\newcommand{\CommentsR}{1}
\newcommand{\mynote}[2]{\ifnum\Comments=1\textcolor{#1}{#2}\fi}
\newcommand{\mytodo}[2]{\ifnum\Comments=1%
  \todo[linecolor=#1!80!black,backgroundcolor=#1,bordercolor=#1!80!black]{#2}\fi}
\newcommand{\reviewerresponse}[2]{\ifnum\CommentsR=1%
  \todo[linecolor=#1!80!black,backgroundcolor=#1,bordercolor=#1!80!black]{#2}\fi}
\newcommand{\raf}[1]{\mynote{darkgreen}{[RF: #1]}}
\newcommand{\raft}[1]{\mytodo{green!20!white}{RF: #1}}
\newcommand{\jessie}[1]{\mynote{teal}{[JF: #1]}}
\newcommand{\jessiet}[1]{\mytodo{teal!20!white}{JF: #1}}
\newcommand{\proposedadd}[1]{\mynote{orange}{#1}} % RF: I always read this as "propose dadd"
\newcommand{\reviewerone}[1]{\reviewerresponse{orange!20!white}{R1: #1}}
\newcommand{\reviewertwo}[1]{\reviewerresponse{blue!20!white}{R2: #1}}
\newcommand{\reviewerthree}[1]{\reviewerresponse{green!20!white}{R3: #1}}
\newcommand{\bo}[1]{\mynote{blue}{[Bo: #1]}}
\newcommand{\botodo}[1]{\mytodo{blue!20!white}{[Bo: #1]}}
\newcommand{\btw}[1]{\mytodo{gray!20!white}{BTW: #1}}%TURN OFF FOR NOW \mytodo{gray}{#1}}
\ifnum\Comments=1               % fix margins for todonotes
  \setlength{\marginparwidth}{0.8in}
\fi
\ifnum\CommentsR=1               % fix margins for todonotes
\setlength{\marginparwidth}{0.8in}
\fi

@@

\newcommand{\cell}{\mathrm{cell}}

@@

\newcommand{\Reg}{\mathrm{Reg}}
\newcommand{\regret}[3]{\Reg_{#1}(#2,#3)}

@@

% \jmlrheading{2023}{accepted with minor revisions}{1-56}{7/22}{?/23}{finocchiaro22a}{Jessie Finocchiaro, Rafael Frongillo, and Bo Waggoner}
\jmlrheading{1}{2023}{1-55}{7/22}{7/22}{finocchiaro22a}{Jessie Finocchiaro, Rafael M. Frongillo, and Bo Waggoner}

@@

\ShortHeadings{Embeddings for Consistent Polyhedral Surrogates}{Finocchiaro, Frongillo, and Waggoner}
\firstpageno{1}

%\title{An Embedding Framework for the Design and Analysis of Consistent Polyhedral Surrogates}
%\author{%
% Jessie Finocchiaro \\
% \texttt{jefi8453@colorado.edu}\\
% University of Colorado Boulder
% \and
% Rafael Frongillo\\
% \texttt{raf@colorado.edu}\\
%  University of Colorado Boulder
% \and
% Bo Waggoner\\
% \texttt{bwag@colorado.edu}\\
%  University of Colorado Boulder
%}
%%\date{%                          % nice hack
%%  % \vspace*{-5pt}
%%  University of Colorado Boulder
%%  \\[15pt]
%%  \today
%%}
\begin{document}
\title{An Embedding Framework for the Design and Analysis of Consistent Polyhedral Surrogates}
\author{\name Jessie Finocchiaro \email jefi8453@colorado.edu \\
	\addr Department of Computer Science\\
	University of Colorado Boulder\\
	Boulder, CO, USA
	\AND
	\name Rafael Frongillo \email raf@colorado.edu \\
	\addr Department of Computer Science\\
	University of Colorado Boulder\\
	Boulder, CO, USA
	\AND
	\name Bo Waggoner \email bwag@colorado.edu \\
	\addr Department of Computer Science\\
	University of Colorado Boulder\\
	Boulder, CO, USA
}

@@

\maketitle

\begin{abstract}%
  We formalize and study the natural approach of designing convex surrogate loss functions via embeddings, for discrete problems such as classification, ranking, or structured prediction. 
  In this approach, one embeds each of the finitely many predictions (e.g.\ rankings) as a point in $\reals^d$, assigns the original loss values to these points, and ``convexifies'' the loss in some way to obtain a surrogate.
  We establish a strong connection between this approach and polyhedral (piecewise-linear convex) surrogate losses:
  every discrete loss is embedded by some polyhedral loss, and every polyhedral loss embeds some discrete loss.
  Moreover, an embedding gives rise to a consistent link function as well as linear surrogate regret bounds.
  Our results are constructive, as we illustrate with several examples.
  In particular, our framework gives succinct proofs of consistency or inconsistency for existing polyhedral surrogates, and for inconsistent surrogates, it further reveals the discrete losses for which these surrogates are consistent.
  We go on to show additional structure of embeddings, such as the equivalence of embedding and matching Bayes risks, and the equivalence of various notions of non-redudancy.
  Using these results, we establish that indirect elicitation, a necessary condition for consistency, is also sufficient when working with polyhedral surrogates.
  % The framework can generally be applied to finite prediction tasks, and is demonstrated on examples including high-confidence classification, structured prediction, ordered partitions, and top-$k$ prediction.
\end{abstract}

@@

When working with a restricted hypothesis class $\H$, as opposed to the set of all measurable functions in Definition~\ref{def:consistency}, then the corresponding notion of consistency (called \emph{$\H$-consistency}) is no longer equivalent to calibration~\citep{long2013consistency,kuznetov2014multiclass,zhang2020convex};
see \S~\ref{sec:conclusion} for further discussion.

@@

\paragraph{Extensions to $\H$-consistency}
\reviewertwo{A}
Throughout, we rely heavily on the fact that calibration is equivalent to consistency when the hypothesis class $\H$ in question is the set of all measurable functions.
% However, consistency is defined by considering the optimal hypothesis over the set of all measurable functions (see \S~\ref{app:consistency}).
Calibration is no longer equivalent to consistency, however, when the hypothesis class $\H$ is restricted.
Consistency in this case is called \emph{$\H$-consistency}.
In classification, calibration can fail to be sufficent for $\H$-consistency even in the realizable setting~\citep{long2013consistency,kuznetov2014multiclass,awasthi2021calibration,awasthi2021finer}.
Realizability and similar assumptions often rule out the conditional label distributions causing inconsistency issues in \S~\ref{sec:applications}.
Under such assumptions, $\H$-consistency essentially reduces to an alignment of the surrogate hypothesis class and the target class $\H$, as mediated by the link function~\citep{zhang2020bayes}.
We expect that our link construction (\S~\ref{subsec:link-consistency}) and characterization (\S~\ref{sec:gener-thick-link}) could help extend these results beyond classification when using polyhedral surrogates.
Work has also begun to derive surrogate regret bounds for restricted classes $\H$, called \emph{$\H$-consistency bounds} \citep{awasthi2022hconsistency,awasthi2022multi}.
% additionally study surrogate regret bounds for $\H$-consistent surrogates for adversarial classification and multi-class classification, though it is unclear how such bounds generalize to general finite prediction tasks.
Here we expect that the linear surrogate regret bounds we derive (\S~\ref{subsec:regret-bounds})
could be applied.

>>>>

\documentclass[twoside,11pt]{article}
\usepackage{jmlr2e}
\PassOptionsToPackage{numbers, compress, sort}{natbib}
\usepackage{geometry}

@@

\usepackage{mathtools, amsmath, amssymb, graphicx, verbatim}
%\usepackage{amsthm}
%\usepackage[thmmarks, thref, amsthm]{ntheorem}
\usepackage{color}
\definecolor{darkblue}{rgb}{0.0,0.0,0.2}
\definecolor{darkgreen}{rgb}{0.0,0.3,0.0}
\hypersetup{urlcolor=darkblue,
            anchorcolor=darkblue,citecolor=darkblue, hidelinks}
\usepackage{wrapfig}
\usepackage[font=small]{caption}
\usepackage{subcaption}
\usepackage[colorinlistoftodos,textsize=tiny]{todonotes} % need xargs for below
%\usepackage{accents}
\usepackage{bbm}
\usepackage{xspace}

@@

\usetikzlibrary{calc}
\newcommand{\Comments}{0}
\newcommand{\CommentsR}{0}
\newcommand{\mynote}[2]{\ifnum\Comments=1\textcolor{#1}{#2}\fi}
\newcommand{\mytodo}[2]{\ifnum\Comments=1%
  \todo[linecolor=#1!80!black,backgroundcolor=#1,bordercolor=#1!80!black]{#2}\fi}
\newcommand{\reviewerresponse}[2]{\ifnum\CommentsR=1%
  \todo[linecolor=#1!80!black,backgroundcolor=#1,bordercolor=#1!80!black]{#2}\fi}
\newcommand{\raf}[1]{\mynote{darkgreen}{[RF: #1]}}
\newcommand{\raft}[1]{\mytodo{green!20!white}{RF: #1}}
\newcommand{\jessie}[1]{\mynote{teal}{[JF: #1]}}
\newcommand{\jessiet}[1]{\mytodo{teal!20!white}{JF: #1}}
\newcommand{\proposedadd}[1]{\mynote{orange}{#1}} % RF: I always read this as "propose dadd"
\newcommand{\reviewerone}[1]{\reviewerresponse{orange!20!white}{R1: #1}}
\newcommand{\reviewertwo}[1]{\reviewerresponse{blue!20!white}{R2: #1}}
\newcommand{\reviewerthree}[1]{\reviewerresponse{green!20!white}{R3: #1}}
\newcommand{\bo}[1]{\mynote{blue}{[Bo: #1]}}
\newcommand{\botodo}[1]{\mytodo{blue!20!white}{[Bo: #1]}}
\newcommand{\btw}[1]{\mytodo{gray!20!white}{BTW: #1}}%TURN OFF FOR NOW \mytodo{gray}{#1}}
\ifnum\Comments=1               % fix margins for todonotes
  \setlength{\marginparwidth}{0.8in}
\fi
\ifnum\CommentsR=1               % fix margins for todonotes
\setlength{\marginparwidth}{0.8in}
\fi

@@

\newcommand{\Reg}{R}
\newcommand{\cell}{\mathrm{cell}}

@@

\newcommand{\regret}[3]{R_{#1}(#2,#3)}

@@

%\jmlrheading{1}{2022}{1-55}{7/22}{7/22}{finocchiaro22a}{Jessie Finocchiaro, Rafael M. Frongillo, and Bo Waggoner}
\usepackage{lastpage}
\jmlrheading{25}{2024}{1-\pageref{LastPage}}{6/22; Revised
1/24}{2/24}{22-0743}{Jessie Finocchiaro, Rafael M. Frongillo, Bo Waggoner}
\ShortHeadings{Embeddings for Consistent Polyhedral Surrogates}{Finocchiaro Frongillo Waggoner}

@@

\firstpageno{1}

%\title{An Embedding Framework for the Design and Analysis of Consistent Polyhedral Surrogates}
%\author{%
% Jessie Finocchiaro \\
% \texttt{jefi8453@colorado.edu}\\
% University of Colorado Boulder
% \and
% Rafael Frongillo\\
% \texttt{raf@colorado.edu}\\
%  University of Colorado Boulder
% \and
% Bo Waggoner\\
% \texttt{bwag@colorado.edu}\\
%  University of Colorado Boulder
%}
%%\date{%                          % nice hack
%%  % \vspace*{-5pt}
%%  University of Colorado Boulder
%%  \\[15pt]
%%  \today
%%}

\begin{document}
\title{An Embedding Framework for the Design and Analysis of Consistent Polyhedral Surrogates}
\author{\name Jessie Finocchiaro \email jefi8453@colorado.edu \\
	\addr Department of Computer Science\\
	University of Colorado Boulder\\
	Boulder, CO, USA
	\AND
	\name Rafael M. Frongillo \email raf@colorado.edu \\
	\addr Department of Computer Science\\
	University of Colorado Boulder\\
	Boulder, CO, USA
	\AND
	\name Bo Waggoner \email bwag@colorado.edu \\
	\addr Department of Computer Science\\
	University of Colorado Boulder\\
	Boulder, CO, USA
}

@@

\maketitle
\begin{abstract}%
  We formalize and study the natural approach of designing convex surrogate loss functions via embeddings, for discrete problems such as classification, ranking, or structured prediction. 
  In this approach, one embeds each of the finitely many predictions (e.g.\ rankings) as a point in $\reals^d$, assigns the original loss values to these points, and ``convexifies'' the loss in some way to obtain a surrogate.
  We establish a strong connection between this approach and polyhedral (piecewise-linear convex) surrogate losses:
  every discrete loss is embedded by some polyhedral loss, and every polyhedral loss embeds some discrete loss.
  Moreover, an embedding gives rise to a consistent link function as well as linear surrogate regret bounds.
  Our results are constructive, as we illustrate with several examples.
  In particular, our framework gives succinct proofs of consistency or inconsistency for existing polyhedral surrogates, and for inconsistent surrogates, it further reveals the discrete losses for which these surrogates are consistent.
  We go on to show additional structure of embeddings, such as the equivalence of embedding and matching Bayes risks, and the equivalence of various notions of non-redudancy.
  Using these results, we establish that indirect elicitation, a necessary condition for consistency, is also sufficient when working with polyhedral surrogates.
  % The framework can generally be applied to finite prediction tasks, and is demonstrated on examples including high-confidence classification, structured prediction, ordered partitions, and top-$k$ prediction.
\end{abstract}

@@

When working with a restricted hypothesis class $\H$, as opposed to the set of all measurable functions in Definition~\ref{def:consistency}, then the corresponding notion of consistency (called \emph{$\H$-consistency}) is no longer equivalent to calibration~\citep{long2013consistency,kuznetov2014multi,zhang2020convex};
see \S~\ref{sec:conclusion} for further discussion.

@@

\paragraph{Extensions to $\H$-consistency}
\reviewertwo{A}
Throughout, we rely heavily on the fact that calibration is equivalent to consistency when the hypothesis class $\H$ in question is the set of all measurable functions.
% However, consistency is defined by considering the optimal hypothesis over the set of all measurable functions (see \S~\ref{app:consistency}).
Calibration is no longer equivalent to consistency, however, when the hypothesis class $\H$ is restricted.
Consistency in this case is called \emph{$\H$-consistency}.
In classification, calibration can fail to be sufficent for $\H$-consistency even in the realizable setting~\citep{long2013consistency,kuznetsov2014multi,awasthi2021calibration,awasthi2021finer}.
Realizability and similar assumptions often rule out the conditional label distributions causing inconsistency issues in \S~\ref{sec:applications}.
Under such assumptions, $\H$-consistency essentially reduces to an alignment of the surrogate hypothesis class and the target class $\H$, as mediated by the link function~\citep{zhang2020bayes}.
We expect that our link construction (\S~\ref{subsec:link-consistency}) and characterization (\S~\ref{sec:gener-thick-link}) could help extend these results beyond classification when using polyhedral surrogates.
Work has also begun to derive surrogate regret bounds for restricted classes $\H$, called \emph{$\H$-consistency bounds} \citep{awasthi2022hconsistency,awasthi2022multi}.
% additionally study surrogate regret bounds for $\H$-consistent surrogates for adversarial classification and multi-class classification, though it is unclear how such bounds generalize to general finite prediction tasks.
Here we expect that the linear surrogate regret bounds we derive (\S~\ref{subsec:regret-bounds})
could be applied.
